Holomorphic field theories and higher algebra

### 2022-11-17 draft.tex
tightened up the final conjecture

We saw that the moduli stacks of classical vacua are not equivalent, due to points with interesting stabilizers.
On the other hand, there is an open locus where the moduli stacks are equivalent:
the semi-stable points of each moduli stack $\cM_{\rm vac}(\cT_{\sfE}(F,N))$ and $\cM_{\rm vac}(\cT_{\sfM}(F,\check{N}))$ \owen{fix description, as it's possibly just the stable locus or (weakly) stable locus}.
This locus agrees with a dense open subset of the GIT quotient, 
and the isomorphism of the moduli spaces determines an isomorphism between the stable locus of each stack.
Let us try to unravel what this equivalence means for the field theories, both classical and quantum.

Consider any semistable point $x$ in $\cM_{\rm vac}(\cT)$ for some holomorphic QCD theory.
We view $x$ as a vacuum, which thus labels a perturbative classical theory describing the behavior of the theory $\cT$ near $x$ in the space of fields. 
For the vacuum $x$, the perturbative theory is equivalent to a holomorphic $\sigma$-model into the formal neighborhood of $x$ inside the moduli stack of vacua. 
We can assemble these perturbative theories into a curved curved $\beta\gamma$ system from $\CC^2$ into~$\cM_{\rm vac}^{ss}$.

\begin{prop}
The semistable locus $\cM_{\rm vac}^{ss}(\cT)$ of the the moduli stack $\cM_{\rm vac}(\cT)$ parametrizes a family of holomorphic field theories on $\CC^2$, 
and this family is isomorphic to the curved $\beta\gamma$ system from $\CC^2$ into~$\cM_{\rm vac}^{ss}(\cT)$.
\end{prop}

The isomorphism of moduli spaces then ensures that there is a dual vacuum $x_D$ to $x$ in the dual theory, and its perturbative theory is equivalent to the perturbative theory for $x$,
because there is an explicit identification of the formal neighborhood of $x$ with the formal neighborhood of $x_D$. 
Thanks to this identification, a quantization of the theory labelled by $x$ determines a quantization of the theory labelled by $x_D$.
Hence on the semistable locus of $\cM_{\rm vac}$, we can guarantee an equivalence of quantizations.

\begin{prop}
The semistable locus $\cM_{\rm vac}^{ss}$ of the the moduli stack $\cM_{\rm vac}$ parametrizes a family of holomorphic field theories on $\CC^2$, 
and this family is isomorphic to the curved $\beta\gamma$ system from $\CC^2$ into~$\cM_{\rm vac}^{ss}$.

The isomorphism between the semistable loci of the two moduli stacks determines an isomorphism between quantizations over those loci.
\end{prop}

This identification breaks down on the unstable locus, raising the following question:
\begin{quote}
At the quantum level, what happens on the unstable locus? 
\end{quote}
Each unstable point labels a theory with a nonabelian gauge group (``enhanced gauge symmetry''),
and hence its quantization is more involved that at a semistable point and depends nontrivially the gauge group.
The mismatch between the moduli stack of classical vacua makes it seem highly unlikely that we obtain an equivalence after quantization.

@@

Recall that the moduli space arises from the moduli stack by affinization.
In other words, we move from studying translation-invariant solutions (the stack) to studying ``states'' (multiplicative linear functionals on the stack of solutions).
The moduli of classical states are isomorphic.
We hope that something similar happens at the quantum level.
In other words, there is a moduli stack of quantum vacua and a moduli space of quantum vacua,
and we hope the spaces are isomorphic.
We sketch the idea as follows.

\begin{dfn}
For a holomorphic QCD theory let $\cM^q_{\rm vac}(F,N)$ denote the stack $\cM_{\rm vac}(F,N)$ equipped with a sheaf with values in factorization algebras on $\CC^2$.
The value at a solution $x$ is a quantization of the observables for the classical perturbative theory labeled by~$x$.
(One could focus, for simplicity, on the sheaf with values in polydiscs algebras.)

Let $M^q_{\rm vac}(F,N)$ denote the global sections over $\cM_{\rm vac}(F,N)$ of this sheaf. 
It is a factorization algebra on~$\CC^2$.
(Again, one could focus, for simplicity, on the polydiscs algebra.)
\end{dfn}

@@

We note that in the physics literature, there are a number of issues that are relevant in this setting.
For instance, there are ``instanton corrections'' that cannot be found by perturbative techniques, although they can be treated in a mathematically precise way. 
It is interesting to wonder how these would appear in the holomorphic setting.

>>>>

We saw that the moduli stacks of classical vacua are not equivalent, due to points with interesting stabilizers.
On the other hand, there is an open locus where the moduli stacks are equivalent:
take the points of each moduli stack $\cM_{\rm vac}(\cT_{\sfE}(F,N))$ and $\cM_{\rm vac}(\cT_{\sfM}(F,\check{N}))$ where the stabilizer is a finite group,
in other words, the stable locus.
We use $\cM_{\rm vac}(\cT)^s$ to denote this open locus in the moduli stack of a theory~$\cT$.
This locus agrees with a dense open subset of the affinization (or GIT quotient), 
and the isomorphism of the moduli spaces determines an isomorphism between the stable locus of each stack.
Let us try to unravel what this equivalence means for the field theories, both classical and quantum.

Consider any stable point $x$ in $\cM_{\rm vac}(\cT)$ for some holomorphic QCD theory.
We view $x$ as a vacuum, which thus labels a perturbative classical theory describing the behavior of the theory $\cT$ near $x$ in the space of fields. 
For the vacuum $x$, the perturbative theory is equivalent to a holomorphic $\sigma$-model into the formal neighborhood of $x$ inside the moduli stack of vacua. 
(This argument is a version of the Higgs mechanism, as phrased using the BV formalism.
See \cite{EG} for an expository account.)
We can assemble these perturbative theories into a holomorphic $\sigma$-model from $\CC^2$ into~$\cM_{\rm vac}^{s}$,
using the methods of~\cite{GGW, WilThesis}.

\begin{prop}
For each holomorphic QCD theory $\cT$, 
the stable locus $\cM_{\rm vac}(\cT)^s$ of its moduli stack parametrizes a family of holomorphic field theories on $\CC^2$, 
and this family is isomorphic to the holomorphic $\sigma$-model from $\CC^2$ into~$\cM_{\rm vac}(\cT)^s$.
\end{prop}

\owen{Is that true?}

This result tells us that, over the stable locus, the observables of a holomorphic QCD theory agree with a sheaf of two-dimensional chiral differential operators, as discussed in \owen{reference section of this paper}.

The isomorphism of moduli spaces then ensures that there is a dual vacuum $x_D$ to $x$ in the dual theory, and its perturbative theory is equivalent to the perturbative theory for $x$,
because there is an explicit identification of the formal neighborhood of $x$ with the formal neighborhood of $x_D$. 
Thanks to this identification, a quantization of the theory labelled by $x$ determines a quantization of the theory labelled by $x_D$.
Hence on the stable locus of $\cM_{\rm vac}$, we can guarantee an equivalence of quantizations.

\begin{prop}
There is an isomorphism of these holomorphic $\sigma$-models for the electric theory $\cT_{\sfE}(F,N)$ and the magnetic theory $\cT_{\sfM}(F,\check{N})$, lifting the isomorphism between their moduli spaces.

This isomorphism determines an isomorphism between quantizations of these holomorphic $\sigma$-models, and hence between quantizations of the holomorphic QCD theories over the stable loci.
\end{prop}

In other words, Eager's conjecture is true over the stable loci: there is an isomorphism of sheaves of two-dimensional chiral differential operators.

This identification breaks down on the non-stable locus, raising the following question:
\begin{quote}
At the quantum level, what happens on the non-stable locus? 
\end{quote}
Each non-stable point labels a theory with a nonabelian gauge group (``enhanced gauge symmetry''),
and hence its quantization is more involved that at a stable point and depends nontrivially the gauge group.
The mismatch between the moduli stack of classical vacua makes it seem highly unlikely that we obtain an equivalence after quantization.

@@

Recall that the moduli space arises from the moduli stack by affinization.
In other words, we move from studying translation-invariant solutions (the stack) to studying ``states'' (multiplicative linear functionals on the stack of solutions).
The moduli of classical states are isomorphic.
We hope that something similar happens at the quantum level:
there is a moduli stack of quantum vacua and a moduli space of quantum vacua,
and we hope the spaces are isomorphic.
We sketch the suggestion as follows.

\begin{dfn}
For a holomorphic QCD theory let the {\em moduli stack of quantum vacua} $\cM^q_{\rm vac}(F,N)$ mean the stack $\cM_{\rm vac}(F,N)$ equipped with a sheaf with values in factorization algebras on $\CC^2$.
The value at a solution $x$ is a quantization of the observables for the classical perturbative theory labeled by~$x$.
(One could focus, for simplicity, on the sheaf with values in polydiscs algebras.)
\end{dfn}

Bear in mind an important feature of this sheaf.
Working on the stable locus $\cM_{\rm vac}(F,N)^{s}$, 
we note that the sheaf of classical observables (as a sheaf with values in factorization algebras) has the property that its factorization homology on $\CC^2$ is the sheaf of {\em jets} of functions on $\cM_{\rm vac}(F,N)^{s}$.
This sheaf has a natural flat connection, sometimes called the Grothendieck connection, and the horizontal sections are the structure sheaf $\cO$ of $\cM_{\rm vac}(F,N)^{s}$.
In fact, as shown in \cite{GGW, WilThesis}, this flat connection makes sense even at the level of the factorization algebra,
and not just on factorization homology.
When we quantize, we wish to lift this flat connection as well.

In fact, we expect that a version of this relationship extends to the whole stack $\cM_{\rm vac}(F,N)$,
by using the methods of \cite{CPTVV}.
In formulating the definition above, we are assuming that expectation holds.

We now posit the following.

\begin{dfn}
Let {\em moduli space of quantum vacua} $M^q_{\rm vac}(F,N)$ mean the global horizontal sections over $\cM_{\rm vac}(F,N)$ of this sheaf. 
It is a factorization algebra on~$\CC^2$.
(Again, one could focus, for simplicity, on the polydiscs algebra.)
\end{dfn}

@@

\begin{rmk}
We note that in the physics literature, there are a number of issues that are relevant in this setting.
For instance, there are ``instanton corrections'' that cannot be found by perturbative techniques, although they can be treated in a mathematically precise way. 
It is interesting to wonder how these would appear in the holomorphic setting.
\end{rmk}
